The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-09-27 article.tex
Condition on the number of triggered events

The MBD model has 4 parameters, depicted in table \ref{table:parameters}. 
We pick values of $\nu$ in such a way we expect a multiple speciation
event to be triggered zero ($\nu = 0$), once, twice, four and eight times 
\richel{I assume you can calculate the correct $\nu$}.
We pick values of $q$ that are 0.0 (a speciation barrier at the
triggered event), 0.25, 0.5 and 1.0.
We set our extinction rate $\mu$ to 0.1 in all simulation.
As we select our phylogenies on their number of lineages,
we calculate $\lambda$ in a such a way that the mean expected number
of lineages equals the desired numbers of taxa of 50, 100 and 200. 
For $\nu = 0$, the model falls back to a standard BD model.
Note that the $\lambda$ and $q$ have different units
and it is a misconception to think that for $\lambda = q$ (already
impossible due to their units) the MBD model would reduce to a BD model.

@@

We produce one data set as a comma-separated file.
The general data set has ?144 \richel{recalc} different combinations
of biological parameter combinations, site and clock models.
The data set to investigate sampling has ?552 \richel{recalc} different combinations
of biological parameter combinations, site models, clock models 
and sampling methods. The experiment is computationally intensive:
pilot experiments show that the experiment takes roughly 100 days
of CPU time and 20 days of wall clock time (which includes the queued 
waiting for computational resources) per replicate. 
Due to this, we choose to perform ten replicates, so that the complete
experiment will take an acceptable time of roughly seven months.

We display the data set as an nLTT statistics distribution per
parameter combination as a violin plot.
We only show the nLTT distributions
that were generated under the (correct) assumptions of a Jukes-Cantor site model
and a strict clock model, separated per sampling method used. 
We display the nLTT statistic distributions separated per site or clock model 
in the supplementary information.

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_general.png}
  \caption{
    nLTT statistic distribution per biological parameter set, using the
    general data set, 
    under the (correct) assumptions of a strict clock and Jukes-Cantor site model.
  }
\end{figure}

@@

% Bibliography
\gio{bibliography is missing. The only bib file present does not correspond to the bibliography showed in the pdf file.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MEE style
\bibliographystyle{mee}
\bibliography{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The MBD model has 4 parameters, depicted in table \ref{table:parameters}. 
We pick values of $\nu$ in such a way we expect a multiple speciation
event to be triggered zero ($\nu = 0$), once, twice , four and eight times 
\richel{I assume you can calculate the correct $\nu$}. For each
expected number of triggered events, we only keep those phylogenies
that actually realized the expected number of triggered events.
We pick values of $q$ that are 0.0 (a speciation barrier at the
triggered event), 0.25, 0.5 and 1.0.
We set our extinction rate $\mu$ to 0.1 in all simulation.
As we select our phylogenies on their number of lineages,
we calculate $\lambda$ in a such a way that the mean expected number
of lineages equals the desired numbers of taxa of 50, 100 and 200. 
For $\nu = 0$, the model falls back to a standard BD model.
Note that the $\lambda$ and $q$ have different units
and it is a misconception to think that for $\lambda = q$ (already
impossible due to their units) the MBD model would reduce to a BD model.

@@

We produce one data set as a comma-separated file.
The general data set has ?144 \richel{recalc} different combinations
of parameter combinations.
The experiment is computationally intensive:
pilot experiments show that the experiment takes roughly 100 days
of CPU time and 20 days of wall clock time (which includes the queued 
waiting for computational resources) per replicate. 
Due to this, we choose to perform ten replicates, so that the complete
experiment will take an acceptable time of roughly seven months.

We display the data set as an nLTT statistics distribution per
parameter combination as a faceted violin plot, showing
the effect of the number of species (a proxy for the amount of 
information), the number of triggered events and the intensity of such
a triggered event.
We only show the nLTT distributions
that were generated under the (correct) assumptions of a Jukes-Cantor site model
and a strict clock model, separated per sampling method used. 
We display the nLTT statistic distributions separated per site or clock model 
in the supplementary information.

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_general.png}
  \caption{
    nLTT statistic distribution per setup,
    under the (correct) assumptions of a strict clock and Jukes-Cantor site model.
  }
\end{figure}

@@

% Bibliography
\gio{bibliography is missing. The only bib file present does not correspond to the bibliography showed in the pdf file.}
\richel{Weird. I see it both locally and on Overleaf. Sent email with my screenshots, show me yours to see if I can help}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MEE style
\bibliographystyle{mee}
\bibliography{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
